Re-visiting the Political Deepfake Videos Misinformation the Public But No More than Other Fake Media (2021)

### 2021-03-24 outputs/paper/Paper3_Output.Rmd
fix figure sizing

\begin{equation}
Believei = $$\tau$$iAgegroupi+$$\beta$$Xi+$$\varepsilon i$$
\end{equation}

@@

```{r fig01, fig.cap="Marginal Means in Exposure Experiment Deception Outcomes", echo = FALSE, warning=FALSE, fig.align = "center", out.width="80%",fig.width=10, fig.height=40, regfloat=TRUE}
knitr::include_graphics(here::here("figures/topline_exp1_a.pdf"))
```

\@ref(fig:fig01)) shows the mean level of deception in each age group where the outcome is the extent of believing the clipping is fake or doctored, on a scale of 1-5. The p-values are respectively 0.392, 0.7338, 0.8289, and 0.8863 when we compare the 18-24 age group with age 25-34, age 35-44, age 45-64, and age 65+.  Finally the regression results of extent of belief on age groups and covariates are presented in [ref: Table 1].

```{r fig02, fig.cap="Marginal Means in Exposure Experiment Affect Outcomes",echo = FALSE, warning=FALSE, fig.align = "center", out.width="80%",fig.width=10, fig.height=40, regfloat=TRUE}

#knitr::include_graphics(here::here("figures/topline_exp1_b_2.pdf"))
```

We then want to examine the favorability heterogeneity for different subgroups. From the topline null results shown in the \@ref(fig:fig02)), we can see that young respondents are easier to be affectively triggered by fake clippings than participants aging between 25 and 44, especially presenting a significant difference with the 35-44 age subgroup ($\delta$ = -8.66, $t$= -12.16, $p$ value <0.05). The results also indicate the same finding with what authors have investigated, showing that the elderly are more likely to be affectively triggered by the inveracious media clippings than the young people ($\delta$ =3.42, $t$ =2.0196, $p$ value <0.05). The results regression model [Table 2] also shows the same insights.

@@

\@ref(fig:fig03)) shows the overall accuracy of detecting fake videos as well as accuracy in the five age groups (18-24, 25-34, 35-44, 45-64, 65+), along with associated false positive and false negative rates in the second detection experiment. Table[4] consists of 6 regression models and shows the predictors of the second experiment detection accuracy including six age groups that involved in the detection experiment. Since our research question is to examine the differences between age groups and detection accuracy of deepfake videos, only the 45 to 65 age group is statistically significant compared to its peers.

@@

## Applendix C
```{=latex}

@@

## Applendix D
```{=latex}

\begin{table}[!htbp] \centering 
  \caption{\textbf{Predictors of Second-Stage False Positive Rate (FPR)}} 
  \label{secondstage_fpr} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & \multicolumn{6}{c}{\normalsize Detection FPR (\% Real Videos Classified as Deepfakes)} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 Digital Literacy &  & $-$0.11$^{***}$ & $-$0.09$^{***}$ & $-$0.12$^{***}$ & $-$0.06$^{**}$ & $-$0.09$^{***}$ \\ 
  &  & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\ 
  Accuracy Prompt & $-$0.01 &  & 0.004 & $-$0.01 & 0.003 & $-$0.01 \\ 
  & (0.01) &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Stage 1 Debrief &  &  & $-$0.03$^{***}$ & $-$0.03$^{***}$ & $-$0.03$^{***}$ & $-$0.03$^{***}$ \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Stage 1 Info Provided &  &  & 0.01 & $-$0.0003 & 0.01 & 0.004 \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Political Knowledge &  &  & $-$0.12$^{***}$ & $-$0.11$^{***}$ & $-$0.12$^{***}$ & $-$0.12$^{***}$ \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Internet Usage &  &  & $-$0.004 & $-$0.002 & $-$0.004 & $-$0.002 \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Low-fake Env. &  &  & 0.03$^{***}$ & 0.02$^{***}$ & 0.02$^{***}$ & 0.01 \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  No-fake Env. &  &  & 0.23$^{***}$ & 0.23$^{***}$ & 0.22$^{***}$ & 0.21$^{***}$ \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Age groups 25-34 &  &  & 0.02 & $-$0.001 & 0.01 & $-$0.01 \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Age groups 35-44 &  &  & 0.01 & $-$0.03$^{*}$ & 0.005 & $-$0.04$^{**}$ \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Age groups 45-64 &  &  & $-$0.02 & $-$0.04$^{***}$ & $-$0.02 & $-$0.05$^{***}$ \\ 
  &  &  & (0.02) & (0.01) & (0.02) & (0.02) \\ 
  Age groups 65+ &  &  & $-$0.0001 & $-$0.03$^{*}$ & 0.002 & $-$0.04$^{**}$ \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  High School &  &  & 0.002 & $-$0.001 & $-$0.02 & $-$0.02 \\ 
  &  &  & (0.03) & (0.02) & (0.04) & (0.02) \\ 
  College &  &  & 0.01 & 0.01 & $-$0.02 & $-$0.01 \\ 
  &  &  & (0.03) & (0.02) & (0.04) & (0.02) \\ 
  Postgrad &  &  & 0.03 & 0.02 & $-$0.001 & 0.01 \\ 
  &  &  & (0.04) & (0.02) & (0.04) & (0.02) \\ 
  Republican &  &  & $-$0.07$^{***}$ & $-$0.09$^{***}$ & $-$0.07$^{***}$ & $-$0.08$^{***}$ \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  CRT &  &  & 0.03 & 0.04 & 0.04 & 0.03 \\ 
  &  &  & (0.03) & (0.03) & (0.03) & (0.03) \\ 
  Republican x CRT &  &  & $-$0.07$^{***}$ & $-$0.06$^{***}$ & $-$0.08$^{***}$ & $-$0.07$^{***}$ \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Ambivalent Sexism &  &  & $-$0.0002 & 0.002 & $-$0.002 & 0.001 \\ 
  &  &  & (0.005) & (0.005) & (0.005) & (0.005) \\ 
  Constant & 0.28$^{***}$ & 0.37$^{***}$ & 0.43$^{***}$ & 0.48$^{***}$ & 0.44$^{***}$ & 0.49$^{***}$ \\ 
  & (0.01) & (0.02) & (0.06) & (0.05) & (0.06) & (0.05) \\ 
 \hline \\[-1.8ex] 
Weighted? &  &  &  & \checkmark &  & \checkmark \\ 
Low-Quality Dropped? &  &  &  &  & \checkmark & \checkmark \\ 
\hline \\[-1.8ex] 
N & 5,495 & 5,495 & 5,494 & 5,494 & 4,869 & 4,869 \\ 
R$^{2}$ & 0.0002 & 0.003 & 0.16 & 0.17 & 0.16 & 0.16 \\ 
Adjusted R$^{2}$ & $-$0.0000 & 0.003 & 0.16 & 0.16 & 0.15 & 0.16 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{7}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\ 
\multicolumn{7}{l}{\textit{Notes}: Reference category for environment is High-fake. Reference category for age group is 18-24. PID pooled for brevity.} \\ 
\end{tabular} 
\end{table}

```{=latex}

\begin{table}[!htbp] \centering 
  \caption{\textbf{Predictors of Second-Stage False Negative Rate (FNR)}} 
  \label{secondstage_fnr} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & \multicolumn{6}{c}{\normalsize Detection FNR (\% Deepfakes Classified as Real Videos)} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 Digital Literacy &  & $-$0.03 & $-$0.03 & $-$0.01 & $-$0.05 & $-$0.02 \\ 
  &  & (0.03) & (0.03) & (0.03) & (0.03) & (0.04) \\ 
  Accuracy Prompt & $-$0.01 &  & $-$0.004 & $-$0.01 & 0.003 & $-$0.002 \\ 
  & (0.01) &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Stage 1 Debrief &  &  & 0.01 & 0.01 & 0.01 & 0.01 \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Stage 1 Info Provided &  &  & $-$0.002 & 0.003 & $-$0.01 & $-$0.002 \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Political Knowledge &  &  & $-$0.002 & $-$0.03 & $-$0.01 & $-$0.03 \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Internet Usage &  &  & 0.02$^{***}$ & 0.01 & 0.02$^{***}$ & 0.02$^{**}$ \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Low-fake Env. &  &  & 0.01 & 0.0002 & 0.01 & $-$0.005 \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  No-fake Env. &  &  & $-$0.001 & 0.02 & $-$0.01 & 0.01 \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Age groups 25-34 &  &  & 0.03 & 0.05$^{**}$ & 0.02 & 0.04$^{*}$ \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Age groups 35-44 &  &  & $-$0.01 & 0.003 & $-$0.01 & 0.003 \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Age groups 45-64 &  &  & 0.03 & 0.04$^{**}$ & 0.02 & 0.04$^{**}$ \\ 
  &  &  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
  Age groups 65+ &  &  & 0.01 & 0.02 & 0.01 & 0.01 \\ 
  &  &  & (0.04) & (0.03) & (0.04) & (0.03) \\ 
  High School &  &  & 0.03 & 0.04 & 0.03 & 0.03 \\ 
  &  &  & (0.04) & (0.03) & (0.04) & (0.03) \\ 
  College &  &  & 0.08$^{*}$ & 0.11$^{***}$ & 0.07 & 0.10$^{***}$ \\ 
  &  &  & (0.04) & (0.03) & (0.05) & (0.03) \\ 
  Postgrad &  &  & $-$0.05$^{**}$ & $-$0.04 & $-$0.06$^{**}$ & $-$0.04 \\ 
  &  &  & (0.02) & (0.03) & (0.03) & (0.03) \\ 
  Republican &  &  & 0.09$^{**}$ & 0.08$^{*}$ & 0.11$^{***}$ & 0.10$^{**}$ \\ 
  &  &  & (0.04) & (0.04) & (0.04) & (0.04) \\ 
  CRT &  &  & 0.02$^{***}$ & 0.02$^{***}$ & 0.01$^{*}$ & 0.01 \\ 
  &  &  & (0.01) & (0.01) & (0.01) & (0.01) \\ 
  Republican x CRT &  &  & $-$0.04$^{***}$ & $-$0.03$^{**}$ & $-$0.05$^{***}$ & $-$0.04$^{**}$ \\ 
  &  &  & (0.01) & (0.02) & (0.02) & (0.02) \\ 
  Ambivalent Sexism & 0.34$^{***}$ & 0.36$^{***}$ & 0.15$^{**}$ & 0.19$^{***}$ & 0.18$^{**}$ & 0.22$^{***}$ \\ 
  & (0.01) & (0.03) & (0.07) & (0.06) & (0.07) & (0.07) \\ 
 \hline \\[-1.8ex] 
Weighted? &  &  &  & \checkmark &  & \checkmark \\ 
Low-Quality Dropped? &  &  &  &  & \checkmark & \checkmark \\ 
\hline \\[-1.8ex] 
N & 3,690 & 3,690 & 3,690 & 3,690 & 3,266 & 3,266 \\ 
R$^{2}$ & 0.0002 & 0.0003 & 0.02 & 0.03 & 0.02 & 0.02 \\ 
Adjusted R$^{2}$ & $-$0.0000 & 0.0000 & 0.02 & 0.03 & 0.01 & 0.02 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{7}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\ 
\multicolumn{7}{l}{\textit{Notes}: Reference category for environment is High-fake. Reference category for age group is 18-24. PID pooled for brevity.} \\ 
\end{tabular} 
\end{table}

```
# Reference

>>>>

\begin{equation}
$$Believei= \tau \times Agegroupi+\beta \times Xi+\varepsilon$$
\end{equation}

@@

```{r fig01, fig.cap="Marginal Means in Exposure Experiment Deception Outcomes", echo = FALSE, warning=FALSE, fig.align = "center", out.width="80%", regfloat=TRUE}
knitr::include_graphics(here::here("figures/topline_exp1_a.png"))
```

\@ref(fig:fig01)) shows the mean level of deception in each age group where the outcome is the extent of believing the clipping is fake or doctored, on a scale of 1-5. The p-values are respectively 0.392, 0.7338, 0.8289, and 0.8863 when we compare the 18-24 age group with age 25-34, age 35-44, age 45-64, and age 65+.  Finally the regression results of extent of belief on age groups and covariates are presented in the Appendix.

```{r fig02, fig.cap="Marginal Means in Exposure Experiment Affect Outcomes",echo = FALSE, warning=FALSE, fig.align = "center", out.width="80%",regfloat=TRUE}

knitr::include_graphics(here::here("figures/topline_exp1_b_2.png"))
```

We then want to examine the favorability heterogeneity for different subgroups. From the topline null results shown in the \@ref(fig:fig02)), we can see that young respondents are easier to be affectively triggered by fake clippings than participants aging between 25 and 44, especially presenting a significant difference with the 35-44 age subgroup ($\delta$ = -8.66, $t$= -12.16, $p$ value <0.05). The results also indicate the same finding with what authors have investigated, showing that the elderly are more likely to be affectively triggered by the inveracious media clippings than the young people ($\delta$ =3.42, $t$ =2.0196, $p$ value <0.05). The results regression model in the Appendix also shows the same insights.

@@

\@ref(fig:fig03)) shows the overall accuracy of detecting fake videos as well as accuracy in the five age groups (18-24, 25-34, 35-44, 45-64, 65+), along with associated false positive and false negative rates in the second detection experiment. Appendix includes predictors of second stage experiment which consist of 6 regression models and shows the predictors of the second experiment detection accuracy including six age groups that involved in the detection experiment. Since our research question is to examine the differences between age groups and detection accuracy of deepfake videos, only the 45 to 65 age group is statistically significant compared to its peers.

@@

## Appendix C
```{=latex}

@@

\newpage
# Reference
